The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-10 paper/ms.tex
Update midplane values

To allow for potential small inaccuracies in the determination of the original
fiducial coordinate system, we also subtract the best fit $\text{A}
\sin{\left(\phi + \text{B}\right)} + \text{C}$ curve from the midplane as a
function of azimuth to account for an overall tilt of the midplane (a
simplified version of the strategy described in
\citealt{2019ApJ...871..145A}). For $\text{A}$ the values are $-174$, $62$,
and $3.8\,\pc$, for $\text{B}$ the values are $0.3$, $0.65$, and
$0.021\,\text{rad}$ and for $\text{C}$ the values are $-47$, $18$, and
$-15\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. For the assumed solar
radius of $8.2\,\kpc$, we can approximate the angle offset for the $z$-axis
from the values of $\text{A}$ --- we compute $1.22$, $0.43$, and $0.03\,\deg$
for \mi{}, \mf{}, and \mm{}. These angle offsets are consistent with the
values given in \citet{2018arXiv180610564S} for the difference between the
$z$-axis as defined by the gas and stars.

>>>>

To allow for potential small inaccuracies in the determination of the original
fiducial coordinate system, we also subtract the best fit $\text{A}
\sin{\left(\phi + \text{B}\right)} + \text{C}$ curve from the midplane as a
function of azimuth to account for an overall tilt of the midplane (a
simplified version of the strategy described in
\citealt{2019ApJ...871..145A}). For $\text{A}$ the values are $-165$, $45$,
and $8.8\,\pc$, for $\text{B}$ the values are $0.67$, $-0.088$, and
$0.031\,\text{rad}$ and for $\text{C}$ the values are $-69$, $19$, and
$-18\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. For the assumed Solar
radius of $8.2\,\kpc$, we can approximate the angle offset for the $z$-axis
from the values of $\text{A}$ --- we compute $1.15$, $0.31$, and $0.06\,\deg$
for \mi{}, \mf{}, and \mm{}. These angle offsets are consistent with the
values given in \citet{2018arXiv180610564S} for the difference between the
$z$-axis as defined by the gas and stars.
